### 2015-08-28 fundamentals/conclusion.tex
fixes #128

Similarly, the fidelity-agnostic, modular \Cyclus architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. To support this, the \Cycamore library provides models 
employing basic physics for core fuel cycle facilities and extension libraries 
from the community more support detailed simulations. Indeed, agents of such 
varying fidelity can even exist in the same simulation. Researchers no longer 
need to reinvent the underlying simulator framework in order to model a simulation 
focused on the aspects of the fuel cycle relevant to their research.

>>>>

Similarly, the fidelity-agnostic, modular \Cyclus architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all (though the user must explicitly turn off radioactive decay of 
materials if that is desired). To support this, the \Cycamore library provides models 
employing basic physics for core fuel cycle facilities and extension libraries 
from the community support more detailed simulations. Indeed, agents of such 
varying fidelity can even exist in the same simulation. Researchers no longer 
need to reinvent the underlying simulator framework in order to model a simulation 
focused on the aspects of the fuel cycle relevant to their research.
